Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-26 manuscript.tex
figure 3 adjust caption + macrostate numbers

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that the most probable state $\mathcal{S}_5$ acts as a transition state for transitions between states $\mathcal{S}_2$ and $\mathcal{S}_4$.
(e) The Trp-1 SASA shows high variance for all macrostates except $\mathcal{S}_1$ in which the Trp-1 shows the lowest exposure to the solvent.
(f) The Trp-1 SASA autocorrelation function yields a weak signal (top) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (bottom).
(g) Superimposed cartoon representations of $200$ molecular conformations sampled from each of the four macrostates show that the backbone appears to obstruct the Trp-1 exposure to the solvent in $\mathcal{S}_{(1,2)}$ but less so in $\mathcal{S}_{(3,4)}$.}
\label{fig:msm-analysis}
\end{figure}

@@

TPT~\cite{weinan-tpt,metzner-msm-tpt} is a method used to analyze the statistics of transition pathways. The TPT version of~\cite{noe-folding-pathways} can be conveniently applied to the estimated MSM. Here, we compute the TPT flux between macrostates $\mathcal{S}_2$ and $\mathcal{S}_4$ (Fig.~\ref{fig:msm-analysis}d).
The committor projection onto the first two TICA components shows that it is constant within the metastable states defined above.
Transition regions (macrostate $\mathcal{S}_4$) can be identified by committor values $\approx \frac{1}{2}$.

>>>>

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that the most probable state $\mathcal{S}_5$ acts as a transition state for transitions between states $\mathcal{S}_2$ and $\mathcal{S}_4$.
(e) The Trp-1 SASA autocorrelation function yields a weak signal (top) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (bottom).}
\label{fig:msm-analysis}
\end{figure}

@@

TPT~\cite{weinan-tpt,metzner-msm-tpt} is a method used to analyze the statistics of transition pathways. The TPT version of~\cite{noe-folding-pathways} can be conveniently applied to the estimated MSM. Here, we compute the TPT flux between macrostates $\mathcal{S}_2$ and $\mathcal{S}_4$ (Fig.~\ref{fig:msm-analysis}d).
The committor projection onto the first two TICA components shows that it is constant within the metastable states defined above.
Transition regions (macrostates $\mathcal{S}_{(1,5)}$) can be identified by committor values $\approx \frac{1}{2}$.
